

```{r preliminary_code}

library(dplyr)
library(data.table)
library(ggplot2)
library(ISLR)
library(tidyverse)
library(tidyr)
library(readr)
library(readxl)
library(gginference)
library(stats)
library(data.table)


airline <- read.csv("airline customer service.csv")



```


## Analyses {.tabset}


The primary research question that we would like to address is: "Does support over phone or online platform lead to differences in the rate of success in resolving customer problems?".

The measurable quantity is the outcome of whether problems were successfully resolved. 


```{r q1}






```






####

Kind of Research that Could be Conducted

#### 

An observational and descriptive study could be conducted with the available data which belongs to the airline's company records on interactions with customers. 

A two samples test of proportion could be applied on the observed data as part of inferential statistics to determine if there is a significant difference in the probability of success in resolving customer problems between phone and online platform inquiries. 


```{r q2}



```






#### 

Drawbacks to the Proposed Study

#### 

Unlike experiments in which we could leverage randomization to allocate subjects into each group, we might encounter selection bias as the test subjects could self-select their groups and hence these groups might not be representative of the population. 

Also, without randomization in an observational study, we could not be certain there there is probabilistic balance between the cohorts. 


```{r q3}




```





### 

####

Performing a stastistical test to analyze the relationship between the independent and dependent variables.

####
I have chosen the two sample proportion test (two-tailed). The independent variable would be the service modality namely online platform and phone. The dependent variable would be the outcome of whether the customer's problem was solved by the agent during the interaction. 

From both tests, the obtained p-value of 3.299e-11 is much smaller than the typical significance level of 0.05. Hence, we could reject the null hypothesis, concluding that there is significant difference in the probability of success in resolving problems between the two groups of inquiries by online platform and phone. 




```{r q5}


prop_test_online_phone <- prop.test(x = c(airline_online_successful, airline_phone_successful), n = c(airline_online_total_count, airline_phone_total_count))

prop_test_online_phone








```





### 

#### 

Incoporating other Variables that could have Significant Effects

#### 

A logistic regression model could be generated with the additional measured variables.

The summary of the model would provide us with an insight on whether these variables are statistically significant in predicting the outcome (i.e. whether the customer's problem would be resolved). 


```{r q7}


```





#### 

Creating a model that estimates the effect of the independent variable on the dependent variable while incorporating the other measured variables

#### 

Based on the list of variables, I have generated a logistic model with "resolved" as the dependent variable and the rest of the variables as independent variables. The estimates and measures of significance are as shown in the output. 





```{r q8}


airline_linear_model <- glm(resolved ~., data = airline, family = "binomial")

summary(airline_linear_model)



```



#### 

Citing other concerns with regard to this study and its design

#### 

There would be concerns with regard to the study and design. As this is not a controlled experiment, we could not be certain of the effects of changes to the variables on the outcome. Having a control parameter would help to pinpoint the effects of the independent variables on the outcome. 





```{r q9}



```









#### 

Best way to implement a survey at the end of calls to better understand quality of service 


#### 

At the end of the call, to incentivize customers to take an automated survey, a nominal token of appreciation in the form of discount codes or small gifts could be given to customers who successfully completed the survey and subsequently place orders with the airline. 


```{r q11}

```







#### 

Possible additional topics that to Survey and Reasons for Choosing them

#### 

Three potential topics that could be included are: (a) agent's proficiency in addressing the problems; (b)agent's attitude and professionalism; and (c) tendency to make a purchase or recommend the airline to others. 

The first question on the agent's proficiency in addressing problems would provide insights on whether the specific agents require further training to build up domain specific knowledge. This would help to improve customer service for subsequent engagements. 

The second topic would provide a measure of customer satisfaction in interacting with the airline staff. This is an important quantitative measure that could potentially be used as a metric in the assessment of indivdual's performance. 

The third topic could provide insights on the net promoter effect of customers. This could be useful for the marketing team which would be interested in expanding the consumer reach and customer base for the airline. 



```{r q12}

```






#### 

Designing a survey question for each of the three identified additional questions.

#### 


A possible survey question for the first topic could be: "How would you rate the agent's proficiency in the area of your concerns?". The possible answers would be three possible choices:(a) "Poor technical knowledge of the matter"; (b) Moderate level of knowledge to explain and resolve the problem"; and (c) Well-versed in handling the matter with clear explanation. A customer's evaluation choice of (a) means that the agent would likely require more training in the domain while a choice of (c) implies that the agent has been exemplary in technical knowledge of the matter and would likely be able to resolve the problems with ease. 

For the second topic, a possible question could be: "Based on a scale of 1 to 5, where 1 is bad service, 3 is moderate service and 5 is excellent service, how would you rate the agent's attitude and professionalism?". The possible answers would range from 1 to 5. A score of 1 would mean that the customer had a bad experience that could be attributed to poor services rendered by the agent while a score of 5 would imply that the customer likely had a wonderful experience stemming from excellent services provided to him or her. 

A possible question for the third topic could be: "Are you likely to promote our airline to others around you?". The possible answers would be "Yes" or "No". A response of "Yes" means that the customer is generally satisfied with the airline services and would likely convey good words about the airline to others, potentially bringing in new customers. On the other hand, a response of "No" means that the customer is likely unhappy with the airline and would not promote it to others. In more severe cases, the customers might even cite examples of poor experience to others, potentially leading to loss in sales. 


```{r q13}

```







#### 

Reliability of information that comes from the automated survey

#### 

While the survey is available to each user at the end of the call, certain groups of people would be more likely and less likely to respond to it. Hence, the results would be skewed towards the observations of customers who are more likely to respond to the survey. Hence, it would not be as reliable as a survey that is served and completed by a randomly sampled group of people. 





#### 

Other recommendations to help achieve the goal of understanding the quality of its work and the overall satisfaction of the customer

#### 

The managers could consider implementing a follow-up mechanism such as automated emails that would be dispatched within one week from the inquiries. . 

In addition, the managers could consider interviewing a small pool of users as part of the follow-up process to validate the results. Through the interviews, more peripheral questions such as products preferences and frequency of purchases could be included to collect useful attributes for further analysis.

